Experiment 1 Analysis

### 2023-07-27 Analysis/e1_Analysis.qmd
test plots and gam code

```{r setup}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt)
e1 <- readRDS(here("data/e1_07_04_23.rds"))
source(here("Functions/Display_Functions.R"))

@@

>>>>

```{r setup}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,gghalves)
e1 <- readRDS(here("data/e1_07_04_23.rds"))
source(here("Functions/Display_Functions.R"))

train <- e1 |> filter(expMode %in% c("train"))
trainAvg <- train %>% group_by(id, condit, vb, bandInt,trainStage) %>%
  summarise(vx=mean(vx),dist=mean(dist))
test <- e1 |> filter(expMode %in% c("test-Nf","test-train-nf"))
testAvg <- test %>% group_by(id, condit, vb, bandInt) %>%
  summarise(vx=mean(vx),dist=mean(dist),sdist=mean(sdist))

@@

```{r}
#| fig-height: 11
#| fig-width: 12
#| 
rectWidth=.4
vbRect<- e1 %>% group_by(vb) %>% 
  summarise(lowBound=first(bandInt),highBound=first(highBound)) %>% mutate(vbn=as.numeric(vb),
                  vbLag=vbn-rectWidth,vbLead=vbn+rectWidth)

e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |>  ggplot(aes(x = condit, y = vx,fill=vb)) + 
  ggdist::stat_halfeye()

vbRect<- e1 |> group_by(vb) |>
  summarise(lowBound=first(bandInt),highBound=first(highBound)) |> 
  mutate(vbn=as.numeric(vb), rectWidth=.2,
                  vbLag=vbn-rectWidth,vbLead=vbn+rectWidth)

e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |>  
  ggplot(aes(x = vb, y = vx,fill=vb)) + 
  ggdist::stat_halfeye(alpha=.5) + 
  geom_rect(data=vbRect,aes(xmin=vbLag,xmax=vbLead,ymin=lowBound,ymax=highBound,fill=vb),alpha=.3,inherit.aes = FALSE)+
  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2400,by=200),2)) +
  geom_segment(data=vbRect, aes(x=vbLag,xend=vbLead,y=highBound,yend=highBound),alpha=1,linetype="dashed")+
  geom_segment(data=vbRect, aes(x=vbLag,xend=vbLead,y=lowBound,yend=lowBound),alpha=1,linetype="dashed")+
  geom_text(data=vbRect,aes(x=vbLag-.03,y=lowBound+100,label=vb),angle=90,size=3.5,fontface="bold")

testAvg |>  
  ggplot(aes(x = vb, y = vx,fill=vb)) + 
  ggdist::stat_halfeye(alpha=.5,width=.7) + 
  geom_rect(data=vbRect,aes(xmin=vbLag,xmax=vbLead,ymin=lowBound,ymax=highBound,fill=vb),alpha=.3,inherit.aes = FALSE)+
  facet_wrap(~condit,ncol=1)+
  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
  geom_segment(data=vbRect, aes(x=vbLag,xend=vbLead,y=highBound,yend=highBound),alpha=1,linetype="dashed",inherit.aes = FALSE)+
  geom_segment(data=vbRect, aes(x=vbLag,xend=vbLead,y=lowBound,yend=lowBound),alpha=1,linetype="dashed",inherit.aes = FALSE)+
  geom_text(data=vbRect,aes(x=vbLag-.03,y=lowBound+100,label=vb),angle=90,size=5.5,fontface="bold",inherit.aes = FALSE)

# testAvg |>  
#   ggplot(aes(x = vb, y = sdist,fill=vb)) + 
#   ggdist::stat_halfeye(alpha=.5,width=.7) + 
#   facet_wrap(~condit,ncol=1)
# 
# 
# testAvg |>  
#   ggplot(aes(x = vb, y = dist,fill=vb)) + 
#   ggdist::stat_halfeye(alpha=.5,width=.7) + 
#   facet_wrap(~condit,ncol=1)
# 
#

```{r}
#| fig-height: 11
#| fig-width: 12
#| 
sumStats2 = test %>% group_by(id,condit,vb) %>%
  summarise(distMean=mean(dist),distMedian=median(dist),distSd=sd(dist)) %>%group_by(condit,vb) %>%
  summarise(groupMean=round(mean(distMean),0),groupMedian=round(mean(distMedian),0),groupSd=round(mean(distSd),0)) %>%
  mutate(meanLab=paste0("Mean=",groupMean),medianLab=paste0("Median=",groupMedian),sdLab=paste0("Sd=",groupSd)) %>%
  mutate(sumStatLab=paste0(meanLab,"\n",medianLab,"\n",sdLab))

sumStats = test %>% group_by(id,condit,vb) %>%
  summarise(distMean=mean(vx),distMedian=median(vx),distSd=sd(vx)) %>%group_by(condit,vb) %>%
  summarise(groupMean=round(mean(distMean),0),groupMedian=round(mean(distMedian),0),groupSd=round(mean(distSd),0)) %>%
  mutate(meanLab=paste0("Mean=",groupMean),medianLab=paste0("Median=",groupMedian),sdLab=paste0("Sd=",groupSd)) %>%
  mutate(sumStatLab=paste0(meanLab,"\n",medianLab,"\n",sdLab))

bandLines4 <- list(geom_segment(data=vbRect,aes(x=vbLag,xend=vbLead,y=highBound,yend=highBound),alpha=1,linetype="dashed"),
                   geom_segment(data=vbRect,aes(x=vbLag,xend=vbLead,y=lowBound,yend=lowBound),alpha=1,linetype="dashed"),
                   geom_text(data=vbRect,aes(x=vbLag-.03,y=lowBound+100,label=vb),angle=90,size=2.5,fontface="bold") )

test %>% group_by(id,vb,condit) %>% 
  summarise(vxMean=mean(vx)) %>%
  ggplot(aes(x=vb,y=vxMean,fill=vb))+
  gghalves::geom_half_violin(color=NA)+ # remove border color
  gghalves::geom_half_boxplot(position=position_nudge(x=-0.05),side="r",outlier.shape = NA,center=TRUE, 
                    errorbar.draw = FALSE,width=.25)+
  gghalves::geom_half_point(transformation = position_jitter(width = 0.05, height = 0.05),size=.3,aes(color=vb))+
  facet_wrap(~condit,scale="free_x")+
  geom_rect(data=vbRect,aes(xmin=vbLag,xmax=vbLead,ymin=lowBound,ymax=highBound,fill=vb),alpha=.3,inherit.aes = FALSE)+
  bandLines4+
  #geom_text(data=sumStats,aes(x=vb,y=2100,label = groupMean),size=2, vjust = -0.5)+
  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2))+
  theme(legend.position='none',
        plot.title=element_text(face="bold"),
        axis.title.x=element_text(face="bold"),
        axis.title.y=element_text(face="bold"),
        axis.text.x = element_text(size = 7.5))+
  ylab("Mean X Velocity")+xlab("Target Velocity Band") + 
  ggtitle("Testing Performance (no-feedback) - X-Velocity Per Band")+ 
  geom_text(data=sumStats2,aes(y=2090,label = sumStatLab),size=1.9)

test %>% group_by(id,vb,condit) %>% 
  summarise(distMean=mean(dist)) %>% 
  ggplot(aes(x=vb,y=distMean,fill=vb))+
  geom_half_violin(color=NA)+ # remove border color
  geom_half_boxplot(position=position_nudge(x=-0.05),side="r",outlier.shape = NA,center=TRUE, 
                    errorbar.draw = FALSE,width=.25)+
  geom_half_point(transformation = position_jitter(width = 0.05, height = 0.05),size=.3,aes(color=vb))+
  facet_wrap(~condit,scale="free_x")+
  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2))+
  theme(legend.position='none',
        plot.title=element_text(face="bold"),
        axis.title.x=element_text(face="bold"),
        axis.title.y=element_text(face="bold"),
        axis.text.x = element_text(size = 9.0))+
  ylab("Mean Distance From Boundary")+xlab("Target Velocity Band") + 
  ggtitle("Testing Performance (no-feedback) - Absolute Distance from Boundary")+ 
  geom_text(data=sumStats2,aes(y=1200,label = sumStatLab),size=3,fontface="bold")

```{r}
#| fig-height: 11
#| fig-width: 12
test %>% group_by(sbjCode,condit,vb) %>% 
  summarise(distMean=mean(dist)) %>% 
  ggplot(aes(x=condit,y=distMean,fill=condit))+
  stat_summary(geom="bar",fun=mean,position=position_nudge(x=.21),alpha=.7,width=.2)+
   stat_summary(geom="errorbar",fun.data=mean_se,position=position_nudge(x=.21),alpha=.7,width=.1,)+
  geom_half_violin(position=position_dodge(.5),alpha=.55,color=NA)+ # remove border color
  geom_half_boxplot(position=position_dodge(.5),side="r",outlier.shape = NA,center=TRUE, 
                    errorbar.draw = FALSE,width=.25,alpha=.55)+
  geom_half_point(transformation = position_jitter(width = 0.05, height = 0.05),alpha=.2,size=.3)+
  facet_wrap(~vb,scale="free_x")+
  scale_y_continuous(expand=expansion(add=200),breaks=round(seq(0,2000,by=200),2))+
  theme(legend.position='none',
        plot.title=element_text(face="bold"),
        axis.title.x=element_text(face="bold"),
        axis.title.y=element_text(face="bold"),
        axis.text.x = element_text(size = 9.0))+
  ylab("Mean Distance From Boundary")+xlab("Training Condition") + 
  ggtitle("Testing Performance (no-feedback) - Absolute Distance from Boundary")+ 
  geom_text(data=sumStats2,aes(y=1390,label = sumStatLab),position=position_dodge(.5),size=3,fontface="bold")

test %>% 
  group_by(id,condit,vb) %>%  
  reframe(enframe(quantile(dist, c(0.2, 0.4, 0.6,.8)), "quantile", "dist")) |> 
  pivot_wider(names_from=quantile,values_from=dist,names_prefix="Q_") |>
  group_by(vb,condit) |>
  summarise(across(starts_with("Q"), list(mean = mean)))

```{r}
library(ggforce)

testAvg %>% ggplot(aes(x=dist,y=condit,col=condit))+ geom_point()+facet_col(facets="vb")

testAvg %>% ggplot(aes(x=sdist,y=condit,col=condit))+ geom_boxplot()+facet_col(facets="vb")+geom_vline(xintercept=0)
